Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-11 paper/paper.tex
pass on infra

\section{ES6 design}
\Fix{to appear}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}We
found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

% no-bug low console output

% bug high console output

@@

    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\

@@

    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla

@@

    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\

@@

    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\

@@

    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    

@@

    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
    20 & 7/10 & quickfuzz & JavaScriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & x\\
    21 & 7/10 & quickfuzz & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & x\\    

@@

    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{quickfuzz} & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{x}\\

@@

>>>>

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
The latest version of EcmaScript commonly called ES6

\Fix{to appear}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries. For example, according to the latest version of ES6 specification\cite{es6-spec},
they
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

\Igor{
  We defined if an warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
  considered as a HI group, the stream output came from V8 engine. The error message 
  shows informations related to the assertion code (see at line 2) 
  that thows an Error exception. This case was considered as HI groups and after 
  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}

% bug high console output
This a case of a warning reported as HI priority, the Figure~\ref{} shows
the output console of V8 engine. We consider this case as a HI group due 
the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
throw new Error("Test Failed");
  ^
Error: Test Failed
  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:hi-priority}
\end{figure}

\begin{figure}[h!]
  \centering
\begin{minipage}{.45\textwidth}
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}\vfill
  \begin{minipage}{.45\textwidth}
    \scriptsize
    \lstset{escapeinside={@}{@},
      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
      basicstyle=\ttfamily\scriptsize, boxpos=c,
      numberstyle=\tiny,
      morekeywords={assertEq, var, yield, in, function, 
      typeof, return, throw, new, Error, if},
    }
  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}
  \caption{Warning captured as HI priority.}
  \label{fig:lo-priority}
\end{figure}

% no-bug low console output
\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:lo-priority}
\end{figure}

@@

    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & WebKit    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScript      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & Mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScript   \\

@@

    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & Mozilla

@@

    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{Mozilla}\\

@@

    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScript\\

@@

    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    

@@

    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScript \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & V8\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & WebKit\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & Mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & Webkit\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
    21 & 7/10 & quickfuzz & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\

@@

    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{\crossmark} & Chakra & Confirmed & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{JerryScript}\\

@@

    23 & 7/12 & \crossmark & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
